Duplicate Question Detection using Online Learning

### 2016-11-16 paper/main.tex
sample

\begin{abstract}
%\boldmath
An integral part of OMSCS learning experience are online communities such as Piazza. Piazza is described as a ``Q\&A'' forum which is created for every class\cite{kincaid}. An integral part of many online communities is the concept of ``voting''' to determine popular and useful information. However, Piazza lacks this particular functionality which is on other Q\&A boards like Stackoverflow or Quora.

Being able to understand quality posts can be beneficial for students and instructors, as it will reduce the clutter in the community by allow students to ``see''' important posts in the follow up section of different threads and for instructors to identify potential experts and teaching assistant candidates for future classes. By building a corpus of high quality questions, this could even be extended to develop answers to user questions.

>>>>

\begin{abstract}
%\boldmath
An  integral  part  the learning  experiences for both on-campus and off-campus courses are  online  communities  such  as  Piazza.  Piazza is described as a ``Q\&A'' forum which is created for every class. An integral part of many online communities is the concept of ``voting'' to determine popular and useful information. However in many class orientated forums, this feature is not emphasised as post relevance tends to change relative to course assessments. Creating a way to understand quality posts can be beneficial for students and instructors, as it will reduce the clutter in the community by allow students to "see" important posts in the follow up section of different threads and for instructors to identify potential experts and teaching assistant candidates for future classes.
